Pada praktikum kali ini akan dilakukan klasifikasi pada dataset kriminal di Kota Boston, dengan algoritma  Linear Discriminant Analysis (LDA)

## Package

Silahkan install jika belum ada


```{r eval=FALSE}
instal.package("ISLR")
instal.package("MASS")
instal.package("repr")
instal.package("ggplot2")
```

Memanggil Package

```{r message=FALSE}
library("ISLR")
library("MASS")
library("repr")
library("ggplot2")
library("ROCR")
library(class)
head(Boston)
summary(Boston)
```

## Generate the response variable


```{r}
crime_rate <- rep(0,506)
crime_rate[Boston$crim >median(Boston$crim)]=1
df <- Boston[,-1]
df <- data.frame(df, crime_rate)
df$crime_rate <- as.factor(df$crime_rate)
```

## Exploratory data analysis
```{r}
ggplot(df,aes(x=crime_rate,y=zn, color = crime_rate))+geom_boxplot()+theme_classic()+ 
  labs(title="zoned residential plots vs crime_rate")
ggplot(df,aes(x=crime_rate,y=indus, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title="industrial land plots vs crime_rate")
ggplot(df,aes(x=crime_rate,y=rm, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title="rooms per home vs crime_rate")
ggplot(df,aes(x=crime_rate,y=nox, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title = "nitrogen oxides concentration vs crime_rate")
ggplot(df,aes(x=crime_rate,y=age, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title = "age vs crime_rate")
ggplot(df,aes(x=crime_rate,y=dis, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title = "distance to employment centres vs crime_rate")
ggplot(df,aes(x=crime_rate,y=rad,color = crime_rate))+geom_boxplot()+theme_classic() +
  labs(title = "access to radial highways vs crime_rate")
ggplot(df,aes(x=crime_rate,y=ptratio, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title = "pupil-teacher ratio vs crime_rate")
ggplot(df,aes(x=crime_rate,y=black, color = crime_rate))+geom_boxplot()+theme_classic() +
  labs(title = "proportion of blacks vs crime_rate")
ggplot(df,aes(x=crime_rate,y=lstat, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title = "percentage of low income earners vs crime_rate")
ggplot(df,aes(x=crime_rate,y=medv, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title = "owner occupied houses vs crime_rate")
ggplot(df,aes(x=crime_rate,y=tax, color = crime_rate))+geom_boxplot()+theme_classic()+
  labs(title = "full-value property-tax rate vs crime_rate")
```

## Split the dataset into test and training sets

```{r}
set.seed(1110)
df_split = sort(sample(nrow(df), nrow(df)*0.8)) ## 80% of the dataset randomly selected
train<-df[df_split,]
test<-df[-df_split,]
```



## Linear discriminant analysis (LDA)

```{r}
lda.fit=lda(crime_rate~., data = train)
lda.fit
lda.pred=predict(lda.fit,test)
lda.class =lda.pred$class
table(lda.class, test$crime_rate)
```

### Predictive accuracy of LDA model

```{r}
accuracy.lda <- round(mean(lda.class == test$crime_rate), digits =2)*100
print(paste('Accuracy is ',accuracy.lda,"%"))
print(paste('Test error is ',100-accuracy.lda,"%"))
```


